Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-06 WRITEUP/ms.tex
updated Sec 5 altogether

Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified 
in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
Further interpretation and implication of this is discussed in \Sec{origin}.

@@

\subsection{Origin of the MCs} \label{sec:origin} 
\DL{discuss stuff on Toomre $Q$ maps with clumps identified.}

The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). Overall,
the MCs we identified are much bigger in size and mass than nearby GMCs, 
but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

Note that ....

\subsection{Virial Parameter, Collapse, and high SFR at high-\z} \label{sec:diss2}

It may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
nature of the majority of the molecular gas in \flower and its SFR.
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical MC hierarchy.
Second, due to
turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
large-scale gravitational potential and differential rotation.
This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
MCs \citep{Clark04a, Clark05a}.
Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation.

We note that in a recent study by \citet{Pettitt18a}, the authors report that the virial parameter could be a poor indicator
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation.
In particular, these authors do not find any significant correlations between the virial parameter, cloud mass,
and star formation efficiency ($M_*/M_{\rm cl}$).
Identifying a new diagnostic tool
% would be interesting for the future, but is outside the aim of the present work
is beyond the scope of this paper. Here, we are more interested in
comparing the clouds dynamics with observational studies, and thus,
part of the discussion of this paper is based on virial analysis.

\subsection{MC Dynamics Setting the Mass Scale at EoR} \label{sec:diss3}

%% pressure
%The pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and
%since $P\propto\Sigma^2$).
%In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of
%$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
%The higher $\Sigma_{\rm gas}$ is in turn relates to more massive clouds being formed.
%In fact, a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun 
%are found in nearby gas-rich galaxies such as M64 and M51 \citep{Rosolowsky05a, Koda09a, Colombo14a}.
%%On the other hand, such massive molecular structures are unknown to Local Group galaxies
%%\citep[e.g.,][]{Rice16a}, and are likely the sites
%%from which massive star clusters or OB associations are to be formed.
%{\bf So?}

@@

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of
$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$
yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
The enhanced MCs size-scale compared to local GMCs
is therefore likely a manifestation of gravitational instabilities (resulting from the higher $f_{\rm gas}$), which drives
supersonic turbulence in the ISM.

Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
simulations done at higher resolution (e.g., \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations
since they adopt non-cosmological initial conditions.
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).

>>>>

Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Qeff}, respectively (see \Fig{h2density} for examples of clumps identified 
in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
Further interpretation and implication of this is discussed in \Sec{origin}.

@@

\subsection{Origin and Physical Scales of the MCs} \label{sec:origin} 
The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). Overall,
the MCs we identified are much bigger in size and mass than nearby GMCs, 
but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

@@

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of
$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$
yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
simulations done at higher resolution (e.g., \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations
since they adopt non-cosmological initial conditions.
That said, this is reassuring --- our results are not far off in spite of the resolution ($l\approx$\,30\,pc).

%Note that regions of $Q\lesssim1$ is actually somewhat 
%less than the number of MCs we have identified based on density threshold --- 
%but this has something to do with the dependence on 
%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at 
%MCs identified at the highest $n_{\rm cut}$. \DL{do they overlap?}

% alpha parameters
As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
For the MCs in the satellite galaxies, a lower virial parameter is found 
compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
% pext
As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
The lower virial parameter and external pressure of the sub-MCs
compared to their parent MCs are consistent with
the notion that collapsing structures result from local gravitational
instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales. 
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

For MCs in the satellite galaxies, we find low pressures and virial parameters 
which are comparable to those found in clouds formed in the galactic disks 
($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures,
and thus, \SF is expected to continue 
as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.

The apparently large virial parameters seen in the MCs of \flower can be understood using the 
Toomre $Q$ parameter (\Fig{Q} and \Fig{Qeff}). 
We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
instability against axisymmetric perturbations), but  
further evolution/collapse depends on the dynamics or equation of state of the gas. 
Such fragmentation is expected to take place at the
critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
Second, this fragmentation scale is greater than the typical size of GMCs. This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs
correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales. 
Thus, the high virial parameter found 
for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure 
and rotation) and surface density, indicate that most of them are not collapsing structures. 
As such, some MCs lie in regions of $Q>1$. 
Only in (the denser) regions with a low Toomre $Q$ parameter and 
when energy can be dissipated on a timescale 
that is shorter than the timescale over which it gains energy (e.g., heating) 
correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$
nature of most MCs of \flower and its relatively high SFR.
That is, if most of the molecular gas in \flower are stable against collapse, 
how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
The discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
large-scale gravitational potential and differential rotation.
This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
MCs \citep{Clark04a, Clark05a}.
Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation
and collapse on smaller scales to trigger \SF.
